Left-linear rules in adhesive categories

### 2024-02-13 icalp/fusione.tex
varie cose minori

Still, we can identify a
canonical form for switching derivations.

\begin{restatable}[Canonical form]{corollary}{coCanonical}
  \label{co:canonical}
  Let $\der{D}$ and $\der{D}'$ be derivation sequences. If
  $\der{D} \shifteq[\sigma]\der{D}'$ then there is a switching sequence
  \begin{center}
    $\der{D} = \der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
    \shift{\nu_n} \der{D}_n=\der{D}'$
  \end{center}
  where for each $i \in \interval{n}$ the transpostion $\nu_i  = \transp{k}$ is such that 
  $k = \max \{ j \mid \transp{j} \in \inv{\nu_{i,n}}\}$.\todo{P: $\nu_{i,n} = \sigma \circ \nu_{1,i}$, giusto? forse e' piu' carino}
\end{restatable}

>>>>

Still, we can identify a
canonical form for switching derivations: at each step one can apply a switch to the inversion with higher index.

\begin{restatable}[Canonical form]{corollary}{coCanonical}
  \label{co:canonical}
  Let $\der{D}$ and $\der{D}'$ be derivation sequences. If
  $\der{D} \shifteq[\sigma]\der{D}'$ then there is a switching sequence
  \begin{center}
    $\der{D} = \der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
    \shift{\nu_n} \der{D}_n=\der{D}'$
  \end{center}
  where for each $i \in \interval{n}$ the transposition $\nu_i  = \transp{k}$ is such that 
  $k = \max \{ j \mid \transp{j} \in \inv{\nu_{i,n}}\}$.\todo{P: $\nu_{i,n} = \sigma \circ \nu_{1,i}$, giusto? forse e' piu' carino}
\end{restatable}
